A Topic Model of Climate Change Literature

### 2019-05-06 results.tex
update writing

\begin{figure}[h]
	\begin{center}
		\includegraphics[width=0.5\linewidth]{plots/literature_size/volume_variety.pdf}
		%\captionof{figure}
		\caption{The volume and variety of literature on climate change has grown to unmanageable proportions. Each box represents a document-term matrix (unique documents x unique terms) of the abstracts written in each assessment period. The percentage of documents in which the average word occurs in is given in the key.
		}

		\label{growth}
	\end{center}
\end{figure}

@@

>>>>

%\begin{figure}[h]
%	\begin{center}
%		\includegraphics[width=0.5\linewidth]{plots/literature_size/volume_variety.pdf}
%		%\captionof{figure}
%		\caption{The volume and variety of literature on climate change has grown to unmanageable proportions. Each box represents a document-term matrix (unique documents x unique terms) of the abstracts written in each assessment period. The percentage of documents in which the average word occurs in is given in the key.
%		}
%	
%		\label{growth}
%	\end{center}
%\end{figure}

@@

\subsection{Glossary}

ncep
fco
pfc
otcs
dtr
sres
petm
amf
sf5cf3
clc
cwd
etm
cmip5
cmip3
mofs
sdm
mmms
cop21
c3n4
sdg
indc
